### 2022-08-03 main/chapter_2ljets.tex
begin fleshing out results

\section{Results}
\label{sec:2ljets_results}
Figure~\ref{fig:2ljets_summary_no_sr}
Figure~\ref{fig:2ljets_fit_corrmatrix}
Figure~\ref{fig:2ljets_fit_parameters}
Figure~\ref{fig:2ljets_fit_muti_contourss}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_corrmatrix.pdf}
\caption[
Correlation matrix from the background-only fit to control and signal regions
]{%
Correlation matrix from the background-only fit to control and signal regions,
as estimated by \histfitter.
Parameters with smaller levels of correlation are excluded.
}
\label{fig:2ljets_fit_corrmatrix}
\end{figure}

>>>>

\section{Results}
\label{sec:2ljets_results}

Main results from the $\twoljets$-electroweak search have already been
presented in Section~\ref{sec:2ljets_splash} and sprinkled throughout this
chapter.
This section reports some ancillary results.

\TODO{Discuss and tie these together.}

A pre-fit (fitted to control regions but not signal regions) summary plot
is displayed in Figure~\ref{fig:2ljets_summary_no_sr}.

The correlation matrix of parameters, estimated from the inverse Hessian at
the best fit point and reduced to its most correlated parameters, is displayed
in Figure~\ref{fig:2ljets_fit_corrmatrix}.

All fitted parameters and their marginal error bars are displayed in
Figure~\ref{fig:2ljets_fit_parameters}.

Preliminary projected exclusion contours that separate the use only subsets
of our signal regions to assess their effects are displayed in
Figure~\ref{fig:2ljets_fit_muti_contourss}.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_corrmatrix.pdf}
\caption[
Correlation matrix from the background-only fit to control and signal regions
]{%
Correlation matrix from the background-only fit to control and signal regions,
as estimated by \histfitter.
Parameters with smaller levels of correlation are excluded.
Apologies for the small font size.
}
\label{fig:2ljets_fit_corrmatrix}
\end{figure}
